Taking Dyads Seriously

### 2019-07-12 paper/coverletter/netsMatter_coverLetter.tex
syncing

{Editorial Team of American Political Science Review via submission portal}

@@

In political science, however, the dispute has become quite prevalent. Although we clearly work in the latent space world, this paper is not about engaging or extending the ERGM-latent space discussion. Rather, we evaluate the utility of the AME framework using a simulation based exercise and a replication of three recently published works from the field of International Relations. Through the simulation exercise, we show that in the presence of unobserved dependencies the model is able to provide less biased estimates and better calibrated standard errors than extant approaches in the literature. Next, for nearly all of the replications reestimated using the AME framework we find that the case for the key findings from the original works become much less compelling. Additionally, we show through an out-of-sample cross-validation exercise that the AME approach uniformly outperforms each of the replicated approaches in capturing the data generating process of the event of interest.\\[1ex]

@@

\includegraphics [scale=.8]{/Users/s7m/Dropbox/Finances/signature.png}

>>>>

{Editorial Team of Political Science Research \& Methods via submission portal}

@@

In political science, however, the dispute has become quite prevalent. Although we clearly work in the latent space world, this paper is not about engaging or extending the ERGM-latent space discussion. A piece by Minhas, Hoff, and Ward published this year already delves into the differences between various network approaches. This piece, however, is meant to evaluate the utility of the AME framework using a novel simulation based exercise and a replication of three recently published works from the field of International Relations. Through the simulation exercise, we show that in the presence of unobserved dependencies the model is able to provide less biased estimates and better calibrated standard errors than extant approaches in the literature. Next, for nearly all of the replications reestimated using the AME framework we find that the case for the key findings from the original works become much less compelling. Additionally, we show through an out-of-sample cross-validation exercise that the AME approach uniformly outperforms each of the replicated approaches in capturing the data generating process of the event of interest.\\[1ex]

@@

\includegraphics [scale=.8]{/Volumes/Samsung_X5/Dropbox/Finances/signature.png}
